TBD

### 2021-02-20 outputs/paper/paper.Rmd
Fix the linespacing

* the largest concentration (nearly 60%) of restaurants in the Greater Toronto Area are centralized in downtown Toronto (28.26%), North York (15.78%), and Scarborough (13.74%),
* most restaurants are of medium or larger scale, with seating areas of at least 30, 
* a majority of the restaurants are relatively new (1-4 years old), 
* fast-food/quick service restaurants are most common, followed by casual dining, and then fine dining,
* and UberEats is the most popular food courier service in the city.

@@

>>>>

* the largest concentration (nearly 60%) of restaurants in the Greater Toronto Area are centralized in downtown Toronto (28.26%), North York (15.78%), and Scarborough (13.74%);
* most restaurants are of medium or larger scale, with seating areas of at least 30; 
* a majority of the restaurants are relatively new (1-4 years old); 
* fast-food/quick service restaurants are most common, followed by casual dining, and then fine dining;
* and UberEats is the most popular food courier service in the city.

@@

Questions related to the adjustments of the restaurants during the intervention, such as a menu price, and hours and days of operation (Figures 8-12) show us that:

* most of the restaurants in the control group did not change the menu price, while most of the ones in the treatment group either lowered or raised the menu price;
* and most of the restaurants in the control group did not adjust their hours and days of operation, while most of the ones in the intervention group reduced their operating schedule.

Pearson’s Chi-squared test is used to see if there is a statistically significant difference between the intervention and the adjustments of the restaurants. The test results show that the p-value of each of those adjustments is close to 0 (*p* < 2.2e-16), meaning that there is a high correlation between those two variables. Consequently, it is expected that restaurants will adjust the menu price and reduce their operating schedule if they operate on a delivery and take-out only basis.
